Cryptographic assurance of secrecy and fairness in voting

### 2012-12-06 paper/paper.tex
Rewrite discussion of secrets and trust

\subsection{Keeping secrets}

In each of these key systems, there exists some way to tie a vote back to a voter: there is always
some secret. Ideally, there would be a system wherein a vote could be tallied properly without being
able to reveal who the vote was for.

Admittedly, that would be difficult: if that is the only vote, then ``tallying'' just it would
reveal the candidate for which it was cast. But it would be a worthy goal at least to minimize, if
not eliminate, the amount of data that must be kept secret. Usually it is one or two pieces of data
-- and these systems attempt to mitigate risk by requiring that multiple entities be present in
order to access that secret data.

With each of these systems, there is \emph{still} a significant level of trust placed in the body
holding the election. This is the issue with secrets: \emph{someone} must keep them.

In order for a voting system to be \emph{useful}, it must be feasible given the nature of society
today, and so solutions that rely on, say, personally-maintained keypairs are outside the scope of
a practical system.

In the end, there are as yet no \emph{perfect} verifiable voting systems that achieve both complete
privacy and completely verifiable integrity, as there are always attack vectors (often physical
ones). This has not been seen as a problem by researchers in the past, as physical security is
indeed outside the scope of these systems as they have been developed; but perhaps with further
research into advanced cryptographic schemes we can someday eliminate any state-held secret data and
yet hold a completely verifiable election.

\todo{Remark on the fact that the election itself has a single primary ElGamal keypair.}

>>>>

\subsection{Secrets and trust}

In each of these key systems, there exists some way to tie a vote back to a voter or to a physical
receipt: there is always some secret. Ideally, there would be a system wherein a vote could be
tallied properly without \emph{anyone} being able to reveal the candidate selected on the ballot.
Admittedly, to achieve this would be difficult: in the case of a single vote, ``tallying'' just it
would reveal the candidate for which it was cast. But if a secret \emph{must} be kept, it is
worthwhile to take precautions to minimize risk of compromise.

In both Scantegrity and Helios, the most fundamental secret is a key. In Scantegrity, this is the
seed to the pseudorandom number generator used to create Table P; and in Helios, it is a single
ElGamal keypair used for all encryption/decryption operations during a particular election.

The random seed in Scantegrity is a secret that is shared among a group of members of the election
authority, thereby mitigating risk of compromise.

But in Helios, there is a single private ElGamal key that lives on the server. (Note that the
creators of Helios admit this weakness but choose to overlook it, as it is their goal to make
verifiable voting an accessible technology, even with some costs.)

Furthermore, with each of these systems, there is \emph{still} a significant level of trust placed
in the body holding the election. This is the issue with secrets: \emph{someone} must keep them, and
we must place some trust in that party. In Scantegrity, for example, we must assume that we can
trust at least enough of the secret holders so that the seed cannot be obtained and used
inappropriately.

Public-key encryption could potentially solve some of these issues; however, it is not feasible
today to require each voter to maintain his/her own keypair.
